The truncated KdV framework for modeling anomalous waves induced by abrupt depth changes

### 2019-07-18 WavesData-2019/LatexNotes/notes.tex
NM

%----------------------------------------------%
%% LATEX DEFINITIONS
%----------------------------------------------%

% Basic editing
\newcommand{\tocite}{{\color{blue}(to cite)}}
\newcommand{\vsp}[1]{\vspace{#1 pc} \noindent}
\newcommand{\np}{\newpage \noindent}
% Derivatives
\newcommand{\pd}[2]    { \frac{\partial #1} {\partial #2} }
\newcommand{\ppd}[2]  { \frac{\partial^2 #1}{{\partial #2}^2} }
\newcommand{\pdi}[2] { {\partial_#2} #1 }
\newcommand{\td}[2] { \frac{d #1} { d #2 } }
\newcommand{\grad}{\nabla}
\newcommand {\Lap} {\grad^2}
% Vectors and operators
\newcommand{\bvec}[1]{\ensuremath{\boldsymbol{#1}}}
\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\norm}[1]{\left\| #1 \right\|}
\newcommand{\mean}[1]{\left< #1 \right>}
\newcommand{\eps}{\varepsilon}
\newcommand{\dx}{\, dx}

%\newcommand{\defeq}{\mathrel{\mathop:}=}

% Basic physical parameters and scales
\newcommand{\freqp}{f_p}
\newcommand{\amp}{a}
\newcommand{\ampscale}{A}
\newcommand{\etastd}{\eta_{\text std}}
% Parameters that change crossing the ADC
\newcommand{\depth}{d}
\newcommand{\dup}{\depth_{-}}
\newcommand{\ddn}{\depth_{+}}
\newcommand{\dupdn}{\depth_{\pm}}
\newcommand{\lam}{\lambda}
\newcommand{\lamup}{\lam_{-}}
\newcommand{\lamdn}{\lam_{+}}
\newcommand{\lamupdn}{\lam_{\pm}}
\newcommand{\lamfac}{N}
\newcommand{\drat}{D}
\newcommand{\dratdn}{\drat_+}
\newcommand{\dratupdn}{\drat_{\pm}}
% Statistical quantities
\newcommand{\En}{\mathcal{E}}
\newcommand{\Mo}{\mathcal{M}}
\newcommand{\skw}{\text{skew}}
\newcommand{\skwdn}{\skw_+}
\newcommand{\var}{\text{var}}
\newcommand{\varup}{\var_-}
\newcommand{\vardn}{\var_+}
% Dimensionless parameters
\newcommand{\epsup}{\eps_0}
\newcommand{\delup}{\delta_0}
% Hamiltonian and Gibbs stuff
\newcommand{\uhat}{\hat{u}}
\newcommand{\Ham}{H}
\newcommand{\Hup}{\Ham^{-}}
\newcommand{\Hdn}{\Ham^{+}}
\newcommand{\Hupdn}{\Ham^{\pm}}
\newcommand{\Gibbs}{\mathcal{G}}
\newcommand{\Gup}{\Gibbs^{-}}
\newcommand{\Gdn}{\Gibbs^{+}}
\newcommand{\Gupdn}{\Gibbs^{\pm}}
\newcommand{\thup}{\theta^{-}}
\newcommand{\thdn}{\theta^{+}}
\newcommand{\thupdn}{\theta^{\pm}}
\newcommand{\meanup}[1]{\mean{#1}_{-}}
\newcommand{\meandn}[1]{\mean{#1}_{+}}
\newcommand{\meanupdn}[1]{\mean{#1}_{\pm}}

@@

% Table
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{table}[h]%[htbp]
\begin{center}
\caption{Table of parameters}
\label{paramtable}
\begin{tabular}{l l l}
\hline \multicolumn{3} { c }{Parameters that are constant in a single experiment} \\
\hline Description & Notation and definition & Value in experiments \\
\hline
Peak forcing frequency		& $f_p$						& 2 Hz \\
Upstream depth			& $\dup$						& 12.5 cm \\
Downstream depth			& $\ddn$						& 3 cm (and varied) \\
Characteristic wave amplitude	& $a = \mean{\eta^2}^{1/2} $		& 0.03--0.3 cm \\
Upstream wavelength		& $\lamup = \sqrt{g \dup}/f_p$		& 56 cm \\
Amplitude-to-depth ratio		& $\epsup = a / \dup$			& 0.0024--0.024 \\
Depth-to-wavelength ratio		& $\delup = \dup / \lamup$		& 0.22 \\
Depth ratio				& $\dratdn = \ddn/\dup$			& 0.24 (and varied) \\
\hline \multicolumn{3} { c }{Parameters that change value across ADC} \\
\hline Description & Notation and definition \\
\hline
Local depth			& $\depth$			\\
Local wavespeed		& $c = \sqrt{g \depth}$	\\
Local peak wavelength	& $\lam = \sqrt{gd}/f_p$	\\
Local dimensionless depth		& $\drat = \depth/\dup$	
\end{tabular}
\end{center}
\end{table}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%

@@

\subsection{Derivation with $\lam$ changing across ADC}
This derivation must be faulty, but here it is so that I remember it.
Aha, I think the error is as follows: The matching condition is for $\Hdn$ only, using the two measures. So you have to use the downstream scales, in particular $\lamdn$.

>>>>

%----------------------------------------------------------------------------%
%% LATEX DEFINITIONS
%----------------------------------------------------------------------------%
% Basic editing
\newcommand{\tocite}{{\color{blue}(to cite)}}
\newcommand{\vsp}[1]{\vspace{#1 pc} \noindent}
\newcommand{\np}{\newpage \noindent}
% Derivatives
\newcommand{\pd}[2]    { \frac{\partial #1} {\partial #2} }
\newcommand{\ppd}[2]  { \frac{\partial^2 #1}{{\partial #2}^2} }
\newcommand{\pdi}[2] { {\partial_#2} #1 }
\newcommand{\td}[2] { \frac{d #1} { d #2 } }
\newcommand{\grad}{\nabla}
\newcommand {\Lap} {\grad^2}
% Vectors and operators
\newcommand{\bvec}[1]{\ensuremath{\boldsymbol{#1}}}
\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\norm}[1]{\left\| #1 \right\|}
\newcommand{\mean}[1]{\left< #1 \right>}
\newcommand{\eps}{\varepsilon}
\newcommand{\dx}{\, dx}
% Basic physical parameters and scales
\newcommand{\freqp}{f_p}
\newcommand{\amp}{a}
\newcommand{\ampscale}{A}
\newcommand{\etastd}{\eta_{\text std}}
% Parameters that change crossing the ADC
\newcommand{\depth}{d}
\newcommand{\dup}{\depth_{-}}
\newcommand{\ddn}{\depth_{+}}
\newcommand{\dupdn}{\depth_{\pm}}
\newcommand{\lam}{\lambda}
\newcommand{\lamup}{\lam_{-}}
\newcommand{\lamdn}{\lam_{+}}
\newcommand{\lamupdn}{\lam_{\pm}}
\newcommand{\lamfac}{N}
\newcommand{\drat}{D}
\newcommand{\dratdn}{\drat_+}
\newcommand{\dratupdn}{\drat_{\pm}}
% Statistical quantities
\newcommand{\En}{\mathcal{E}}
\newcommand{\Mo}{\mathcal{M}}
\newcommand{\skw}{\text{skew}}
\newcommand{\skwdn}{\skw_+}
\newcommand{\var}{\text{var}}
\newcommand{\varup}{\var_-}
\newcommand{\vardn}{\var_+}
% Dimensionless parameters
\newcommand{\epsup}{\eps_0}
\newcommand{\delup}{\delta_0}
% Hamiltonian and Gibbs stuff
\newcommand{\uhat}{\hat{u}}
\newcommand{\Ham}{H}
\newcommand{\Hup}{\Ham^{-}}
\newcommand{\Hdn}{\Ham^{+}}
\newcommand{\Hupdn}{\Ham^{\pm}}
\newcommand{\Gibbs}{\mathcal{G}}
\newcommand{\Gup}{\Gibbs^{-}}
\newcommand{\Gdn}{\Gibbs^{+}}
\newcommand{\Gupdn}{\Gibbs^{\pm}}
\newcommand{\thup}{\theta^{-}}
\newcommand{\thdn}{\theta^{+}}
\newcommand{\thupdn}{\theta^{\pm}}
\newcommand{\meanup}[1]{\mean{#1}_{-}}
\newcommand{\meandn}[1]{\mean{#1}_{+}}
\newcommand{\meanupdn}[1]{\mean{#1}_{\pm}}
%----------------------------------------------------------------------------%

@@

% Table
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{table}[h]%[htbp]
\begin{center}
\caption{Table of parameters}
\label{paramtable}
\begin{tabular}{l l l}
\hline \multicolumn{3} { c }{Parameters that are constant in a single experiment} \\
\hline Description & Notation and definition & Value in experiments \\
\hline
Peak forcing frequency		& $f_p$						& 2 Hz \\
Characteristic wave amplitude	& $\etastd = \mean{\eta^2}^{1/2} $		& 0.03--0.3 cm \\
Upstream depth			& $\dup$						& 12.5 cm \\
Downstream depth			& $\ddn$						& 3 cm (and varied) \\
Upstream wavelength		& $\lamup = \sqrt{g \dup}/f_p$		& 56 cm \\
Amplitude-to-depth ratio		& $\epsup = \etastd / \dup$			& 0.0024--0.024 \\
Depth-to-wavelength ratio		& $\delup = \dup / \lamup$		& 0.22 \\
Depth ratio				& $\dratdn = \ddn/\dup$			& 0.24 (and varied) \\
\hline \multicolumn{3} { c }{Parameters that change value across ADC} \\
\hline Description & Notation and definition \\
\hline
Local depth			& $\depth$			\\
Local wavespeed		& $c = \sqrt{g \depth}$	\\
Local peak wavelength	& $\lam = \sqrt{gd}/f_p$	\\
Local dimensionless depth		& $\drat = \depth/\dup$	
\end{tabular}
\end{center}
\end{table}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%

@@

\subsection{Derivation with $\lam$ changing across ADC (Obselete)}
This derivation must be faulty, but here it is so that I remember it.
Aha, I think the error is as follows: The matching condition is for $\Hdn$ only, using the two measures. So you have to use the downstream scales, in particular $\lamdn$.
